Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-08 paper/main.tex
[issue 2.14] change order

The convolutional neural network~\citep[ConvNet;][]{fukushima1980neocognitron,lecun1998gradient}
is a type of deep, feedforward neural network
that has recently become \added{a popular} approach in the computer vision community.
In a typical ConvNet, the first few stages are composed of two types of layers: 
convolutional layers and pooling layers.

@@

A typical pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
Since the pooling layer aggregates the activations of neighboring units from the previous layer,
it reduces the dimensionality of the feature maps and
makes the model invariant to small shifts and distortions.
Two or more layers of convolution and pooling are stacked,
followed by more convolutional and fully-connected layers.

>>>>

The convolutional neural network~\citep[ConvNet;][]{fukushima1980neocognitron,lecun1998gradient}
is a type of deep, feedforward neural network
that has recently become
\added{
a popular
}
approach in the computer vision community.
In a typical ConvNet, the first few stages are composed of two types of layers: 
convolutional layers and pooling layers.

@@

\added{
Typically, a
}
pooling layer computes the maximum of a local $2\times2$ patch in a feature map.
Since the pooling layer aggregates the activations of neighboring units from the previous layer,
it reduces the dimensionality of the feature maps and
makes the model invariant to small shifts and distortions.
Two or more layers of convolution and pooling are stacked,
followed by more convolutional and fully-connected layers.
